### 2021-12-31 dedication/dedication.tex
remove redudant index
init draft of chapter3

% List extra publications
In addition to the above papers, these following publications that I authored/co-authored during my PhD are out of the main scope of this thesis, and are briefly mentioned in the background or future directions.
\begin{enumerate}
	\item Shafa Balaram, Kai Arulkumaran, \underline{Tianhong Dai}, and Anil Anthony Bharath, ``A Maximum Entropy Deep Reinforcement Learning Neural Tracker", International Workshop on Machine Learning in Medical Imaging, 2019.
	\item Yali Du, Lei Han, Meng Fang, \underline{Tianhong Dai}, Ji Liu, and Dacheng Tao, ``LIIR: Learning Individual Intrinsic Reward in Multi-Agent Reinforcement Learning", Advances in Neural Information Processing Systems, 2019.
	\item \underline{Tianhong Dai}, Wei Li, Xilei Cao, Jianzhuang Liu, Xu Jia, Ales Leonardis, Youliang Yan, and Shanxin Yuan, ``Wavelet-Based Network For High Dynamic Range Imaging", Submitted to IEEE Transactions on Imaging Processing, 2021.
\end{enumerate}

>>>>

% List extra publications
In addition to the above papers, these following publications that I authored/co-authored during my PhD are out of the main scope of this thesis, and are briefly mentioned in the background or future directions.
\begin{enumerate}
	\item Cher Bass, \underline{Tianhong Dai}, Benjamin Billot, Kai Arulkumaran, Antonia Creswell, Claudia Clopath, Vincenzo de Paola, and Anil Anthony Bharath, ``Image Synthesis with a Convolutional Capsule Generative Adversarial Network", International Conference on Medical Imaging with Deep Learning, 2019 (Oral).
	\item Shafa Balaram, Kai Arulkumaran, \underline{Tianhong Dai}, and Anil Anthony Bharath, ``A Maximum Entropy Deep Reinforcement Learning Neural Tracker", International Workshop on Machine Learning in Medical Imaging, 2019.
	\item Yali Du, Lei Han, Meng Fang, \underline{Tianhong Dai}, Ji Liu, and Dacheng Tao, ``LIIR: Learning Individual Intrinsic Reward in Multi-Agent Reinforcement Learning", Advances in Neural Information Processing Systems, 2019.
\end{enumerate}
